Mental Health Factors and Covid

### 2025-04-30 products/manuscript/Manuscript.qmd
Part 6 updates

Complex survey design was used to allow for generalizability of results, using variables PSU, STRATA, and SAMPWEIGHT. A summary table was generated to find occurence of each of the factors and their inverses among the data. Next, single models were ran to find associations between each variable with covid test postivity. To explore the data further, a multivariate model, LASSO regression, and a third advanced model (replace this) were ran with cross validation.

@@

@@

>>>>

To examine prevelance of mental health factors among the United States population, compmlex survey design was used to allow for generalizability of results, specifically, variables PSU, STRATA, and SAMPWEIGHT. A summary table was generated to find occurence of each of the factors and their inverses among the data, seen below.

@@

Next, single models were ran to find associations between each variable with covid test postivity. Complex survey design was used to allow generalizability of results to the United States population.

@@

To explore the data further, a multivariate model, LASSO regression, and a third advanced model (replace this) were ran with cross validation.
